\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-07 doc/paper.tex
added paragraph on testing against CE6SSM.
doc/paper.tex: relate a sentence better to the preceding one
update average run-time in the Program Summary

\section{Program Summary}
\noindent{\em Program title:} \fs\\ {\em Program obtainable from:}
         {\tt http://flexiblesusy.hepforge.org/}\\ {\em Distribution
           format:}\/ tar.gz\\ {\em Programming language:} {\tt
           C++, Wolfram/\mathematica, FORTRAN, Bourne shell}\\ {\em Computer:}\/ Personal computer\\ {\em Operating
           system:}\/ Tested on Linux 3.x, MacOS\\
         {\em External routines:}\/ SARAH 4.0.4, Boost library,
         Eigen, LAPACK\\ {\em
           Typical running time:}\/ 0.1-0.3 seconds per parameter
         point.\\ {\em Nature of problem:}\/ Determining the mass
         spectrum and mixings for any supersymmetric model. The
         generated code must find simultaneous solutions to
         constraints which are specified at two or more different
         renormalization scales, which are connected by
         renormalization group equations forming a large set of
         coupled first-order differential equations. \\ {\em Solution method:}\/
         Nested iterative algorithm and numerical minimisation of the
         Higgs potential.  \\ {\em Restrictions:} The couplings must
         remain perturbative at all scales between the highest and
         lowest boundary condition.  \fs~ assumes that all couplings
         of the model are real (i.e.\ $CP-$conserving). Due to the
         modular nature of the generated code adaption and extension
         to overcome restrictions in scope is quite straightforward.

@@

In \secref{sec:changing boundary conditions},
it was explained how one can let \fs generate
an alternative boundary condition class
by authoring a model file.
Nonetheless, the way to employ this class at the C++ level
might still remain obscure to the reader
since \fs automatically took care of it.
Here, an example shall be exhibited
with the emphasis on the modular C++ code structure
that helps programming.
Concretely,
the auto-generated low-energy boundary condition on the MSSM
shall be modified so that
$\alpha_{\text{s},\text{susy}}^{\text{\DRbar}}$
is determined from
$\alpha_{\text{s},\text{SM}}^{(5),\text{\MSbar}}$
by means of a two-loop matching.
This shall be accompanied by an improvement
of the $g_3$ $\beta$-function to the three-loop accuracy.

>>>>

\section{Program Summary}
\noindent{\em Program title:} \fs\\ {\em Program obtainable from:}
         {\tt http://flexiblesusy.hepforge.org/}\\ {\em Distribution
           format:}\/ tar.gz\\ {\em Programming language:} {\tt
           C++, Wolfram/\mathematica, FORTRAN, Bourne shell}\\ {\em Computer:}\/ Personal computer\\ {\em Operating
           system:}\/ Tested on Linux 3.x, MacOS\\
         {\em External routines:}\/ SARAH 4.0.4, Boost library,
         Eigen, LAPACK\\ {\em
           Typical running time:}\/ 0.06-0.2 seconds per parameter
         point.\\ {\em Nature of problem:}\/ Determining the mass
         spectrum and mixings for any supersymmetric model. The
         generated code must find simultaneous solutions to
         constraints which are specified at two or more different
         renormalization scales, which are connected by
         renormalization group equations forming a large set of
         coupled first-order differential equations. \\ {\em Solution method:}\/
         Nested iterative algorithm and numerical minimisation of the
         Higgs potential.  \\ {\em Restrictions:} The couplings must
         remain perturbative at all scales between the highest and
         lowest boundary condition.  \fs~ assumes that all couplings
         of the model are real (i.e.\ $CP-$conserving). Due to the
         modular nature of the generated code adaption and extension
         to overcome restrictions in scope is quite straightforward.

@@

In \secref{sec:changing boundary conditions},
it was explained how one can let \fs generate
an alternative boundary condition class
by authoring a model file.
Nonetheless, the way to employ this class at the C++ level
might still remain obscure to the reader
since \fs automatically took care of it.
Here, an example shall be exhibited
with the emphasis on the modular C++ code structure
that helps such programming tasks.
Concretely,
the auto-generated low-energy boundary condition on the MSSM
shall be modified so that
$\alpha_{\text{s},\text{susy}}^{\text{\DRbar}}$
is determined from
$\alpha_{\text{s},\text{SM}}^{(5),\text{\MSbar}}$
by means of a two-loop matching.
This shall be accompanied by an improvement
of the $g_3$ $\beta$-function to the three-loop accuracy.
